### 2023-09-11 README.Rmd
fix document paths

| **Document** | **Rendered** | **Source** |
|---|---|---|
| Paper | [pdf](documents/paper/paper.pdf) | [rmd](documents/paper/paper.Rmd) |
| Supplementary Materials | [pdf](documents/paper/suppl.pdf) | [rmd](documents/paper/suppl.Rmd) |

>>>>

| **Document** | **Rendered** | **Source** |
|---|---|---|
| Paper | [pdf](documents/output/paper.pdf) | [rmd](documents/paper/paper.Rmd) |
| Supplementary Materials | [pdf](documents/output/suppl.pdf) | [rmd](documents/paper/suppl.Rmd) |
